A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-11-13 docs/results_photometry_v3.01.tex
Corrections in Section 2 and 3

%============================================================================

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in Table \ref{tab:MGEF814W}, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines). The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$. Image scaling and orientation are indicated in the figure. The black line has a length of $10''$ and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.}
\label{fig:MGEinnerRegions}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE \Wilma{[TO DO: How to write Iraf Ellipse???]} model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines). The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black $10''$ orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}). This MGE found from the smooth, symmetric Iraf Ellipse \Wilma{[TO DO]} model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g. spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions by extrapolation the best fit model of the inner regions.}
\label{fig:MGEouterRegions}
\end{figure}

%============================================================================

\begin{table}
\centering
\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by \Wilma{[TO DO: WHO???]}.}
\begin{tabular}{ccc}
\hline
$k$ & $G_k$ & $\delta_k$ [$''$] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{table}

\begin{table*}
\centering
\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:F814W}. The fit is best inside an radius of $5''$. The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in Table \ref{tab:galaxyparameters}. This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.  The first column gives the total F814W luminosity of the Gaussian in Equation \ref{eq:centralItotalL} in units of counts. The second column is the corresponding I-band peak surface brightness in Equation \ref{eq:MGEgeneral} in units of a luminosity surface density, calculated from the first column following the procedure described in Section \ref{sec:MGE_results}. The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \ref{eq:MGEgeneral}.}
\begin{tabular}{cccccc}
\hline
 & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [$''$] & $\sigma_k$ [kpc] & $q'_k$\\\hline
1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
\end{tabular}
\label{tab:MGEF814W}
\end{table*}

%============================================================================

\begin{table*}
\centering
\caption{Galaxy Parameters of J1331}
\begin{tabular}{lllrl}
\hline
redshift                  & $z_d$ & 0.113 & \citep{SWELLSIII}\\
angular diameter distance & $D_d$ [Mpc] & 414 & \\
scaling                   & 1 kpc / 1 $''$ & 2.006 & \\
position angle            & $\phi$ [degrees] & \Wilma{[TO DO: wrt what???]}\\
average axis ratio & $q'$ & 0.598\\
average ellipticity & $\epsilon = 1 - q'$ & 0.402 & \\
apparent I-band magnitude & $m_\text{I}$ [mag] & 15.77 & \\
total I-band luminosity & $L_\text{tot,I}$ [$10^{10} L_\odot$] & 5.6 & \\
effective half-light radius & $R_\text{eff}$ [$''$] & 2.6 & \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\label{tab:galaxyparameters}
\end{table*}

%============================================================================

In Section \ref{sec:results_lensing} we will derive a mass model for J1331 from Lensing. In this section set up a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare in Section \ref{sec:results_lensing} to the mass distribution. The light model will also be the basis of the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
\\To derive J1331's surface brightness distribution, we use the HST image in the infrared F814W filter, shown in Figure \ref{fig:F814W}. In infrared J1331's central old and smooth stellar component is more extended than in the F450W filter in Figure \ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions. In infrared the bulge is also much brighter than the bluish lens images and the imaging is less prone to extinction. The F814W image is therefore best suited for fitting a MGE.

\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image from \Wilma{[TO DO: Where did we get this image from???]}, ignoring diffraction spikes. The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}. The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.

\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5''$ of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}. Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit. J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment. The MGE fit, as performed by the code \cite{Cap02}, splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \ref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it. The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}. The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outside of this.

\paragraph{MGE for the outer regions.} To get an handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF ELLIPSE \Wilma{[TO DO: How to reference???]} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions). Only then we fit a 7-Gaussian MGE to the smooth ellipse model. The MGE does not perfectly reproduce the flattness of the ellipse model at every radius, but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.

\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}, analogous to \Wilma{[TO DO: Cappellari Read me file??? How to reference this???]}
\\The scaling of the drizzled HST/WFC3 images is  $S = 0.05''/$pixel and the total exposure time $T = 1600$ sec. The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of
\begin{equation*}
C_0\text{[counts/pixel]} = \frac{L[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
\end{equation*}
This is then transformed into an I-band surface brightness via
\begin{equation}
\mu_I \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation. $C= 0.1$ corrects for the finite aperture of the WFPC2. And $A_I =0.015$ mag  is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_i$ in mag to the I-band surface density of the Gaussian in $L_\odot$/pc$^2$ as
\begin{eqnarray*}
I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_I \right)},
\end{eqnarray*}
where the term with $z$ accounts for redshift dimming and $M_{\odot,I}=4.08$ mag is the sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_k$[counts] and the corresponding surface brightness density $I \equiv I_{0,k}[L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}. \Wilma{[TO DO: I'm really confused about this. Check, that everything is correct and the naming of quantities, e.g. with or without subscripts of 0, is fine???]}

\paragraph{Inclination.} To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the Iraf Ellipse \Wilma{[TO DO]} model for J1331, which is $q'=0.42$. This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}. If a typical thickness of an oblate disk was around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination would follow from $\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}$ and a correction of $+3^\circ$ \citep{1988ngc..book.....T}. Our estimate for the inclination is therefore $i \approx 70^\circ$. Given this inclination, the 2D MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo}).

\paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is easily determined by summing up the luminosity contributions of all the Gaussians of the MGE for the outer regions (shown as gray lines in Figure \ref{fig:MGEouterRegions}). We find $L_\text{tot,I} \simeq 5.6 \cdot 10^{10} L_\odot$. This corresponds to an apparent magnitude of $m_I = 15.77$ mag. We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions \Wilma{[TO DO: Maybe I need a table anyway???]}, where $R'$ is the projected radius on the sky. We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2 \text{ kpc}$.  All values are summarized in Table \ref{tab:galaxyparameters}.

\Wilma{[TO DO: Reff and Rein are also projected radii. Maybe prime them as well?]}

>>>>

In this section we construct a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare in Section \ref{sec:results_lensing} to the mass distribution. The light model will also be the basis of the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
\\To derive J1331's surface brightness distribution, we use the HST image in the F814W (I-band) filter, shown in Figure \ref{fig:F814W}. At longer wavelengths J1331's central old and smooth stellar component is more extended than in the F450W filter in Figure \ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions. In the I-band the bulge is also much brighter than the bluish lens images and the imaging is less prone to extinction. The F814W image is therefore best suited for fitting a MGE.

\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image, ignoring diffraction spikes. The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}. The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.

%============================================================================
\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in Table \ref{tab:MGEF814W}, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines). The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$. Image scaling and orientation are indicated in the figure. The black line has a length of $10''$ and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.}
\label{fig:MGEinnerRegions}
\end{figure}
%============================================================================

%============================================================================
\begin{table}
\centering
\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by \Wilma{[TO DO: WHO???]}.}
\begin{tabular}{ccc}
\hline
$k$ & $G_k$ & $\delta_k$ [$''$] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{table}
%============================================================================

\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5''$ of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}. Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit. J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment. The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \ref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it. The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}. The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.

%============================================================================
\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF \emph{ellipse} model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines). The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black $10''$ orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}). This MGE found from the smooth, symmetric IRAF \emph{ellipse} model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g. spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions by extrapolation the best fit model of the inner regions. \Wilma{[TO DO: Maybe merge Figures 2 + 3, panels next to each other?]}}
\label{fig:MGEouterRegions}
\end{figure}
%============================================================================

\paragraph{MGE for the outer regions.} To get an handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions). Only then we fit a 7-Gaussian MGE to the smooth ellipse model. The MGE does not perfectly reproduce the flattness of the ellipse model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.

%============================================================================
\begin{table*}
\centering
\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:F814W}. The fit is best inside an radius of $5''$. The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in Table \ref{tab:galaxyparameters}. This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.  The first column gives the total F814W luminosity of the Gaussian in Equation \ref{eq:centralItotalL} in units of counts. The second column is the corresponding I-band peak surface brightness in Equation \ref{eq:MGEgeneral} in units of a luminosity surface density, calculated from the first column following the procedure described in Section \ref{sec:MGE_results}. The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \ref{eq:MGEgeneral}.}
\begin{tabular}{cccccc}
\hline
 & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [$''$] & $\sigma_k$ [kpc] & $q'_k$\\\hline
1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
\end{tabular}
\label{tab:MGEF814W}
\end{table*}
%============================================================================

\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}.
\\The scaling of the drizzled HST/WFC3 images is  $S = 0.05''/$pixel and the total exposure time $T = 1600$ sec. The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of
\begin{equation*}
C_0\text{[counts/pixel]} = \frac{L[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
\end{equation*}
This is then transformed into an I-band surface brightness via
\begin{equation}
\mu_{I,0} \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
\Wilma{[TO DO: Make sure to use $\mu_{I,0}$ where applicable.]} where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation. $C= 0.1$ corrects for the finite aperture of the WFPC2. And $A_I =0.015$ mag  is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_i$ in mag to the I-band surface density of the Gaussian in $L_\odot$/pc$^2$ as
\begin{eqnarray*}
I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0} \right)},
\end{eqnarray*}
where the term with $z$ accounts for redshift dimming and $M_{\odot,I}=4.08$ mag is the sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_k$[counts] and the corresponding surface brightness density $I \equiv I_{0,k}[L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}. \Wilma{[TO DO: I'm really confused about this. Check, that everything is correct and the naming of quantities, e.g. with or without subscripts of 0, is fine???]}

\paragraph{Inclination.} To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the IRAF \emph{ellipse} model for J1331, which is $q'=0.42$. This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}. If a typical thickness of an oblate disk was around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination would follow from 
\begin{equation*}
\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}
\end{equation*}
and a correction of $+3^\circ$ \citep{1988ngc..book.....T}. Our estimate for the inclination is therefore $i \approx 70^\circ$. Given this inclination, the 2D MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo}).

\paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is easily determined by summing up the luminosity contributions of all the Gaussians of the MGE for the outer regions (shown as gray lines in Figure \ref{fig:MGEouterRegions}). We find $L_\text{tot,I} \simeq 5.6 \cdot 10^{10} L_\odot$. This corresponds to an apparent magnitude of $m_I = 15.77$ mag. We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions, where $R'$ is the projected radius on the sky. We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2 \text{ kpc}$.  All values are summarized in Table \ref{tab:galaxyparameters}.
